A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-23 doc/paper1-submission/paper5.tex
Typo fix.

The migration of summary tree construction from treemachine (used for
version 4) to propinquity (for all versions from v5.0 to present) has
increased the pace of synthesis tree releases from the Open Tree of
Life project.  This is partly because the newly available annotations
feature has made it possible to identify which input trees are
responsible for taxa being included or excluded from the summary tree.
Additionally, the new propinquity software pipeline has decreased the decreased
the computational time required to construct a supertree from several
hours to about 8 minutes (after some preprocessing steps which only
have to be performed when the input taxonomy changes).  The amount of
RAM required during tree construction has also decreased substantially.

>>>>

The migration of summary tree construction from treemachine (used for
version 4) to propinquity (for all versions from v5.0 to present) has
increased the pace of synthesis tree releases from the Open Tree of
Life project.  This is partly because the newly available annotations
feature has made it possible to identify which input trees are
responsible for taxa being included or excluded from the summary tree.
Additionally, the new propinquity software pipeline has decreased
the computational time required to construct a supertree from several
hours to about 8 minutes (after some preprocessing steps which only
have to be performed when the input taxonomy changes).  The amount of
RAM required during tree construction has also decreased substantially.
